Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-26 analysis/paper/paper.Rnw
removed orca calls

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
fnsvg <- paste0("Chr", hot_chr, "_heat", ".svg")
fnpdf <- paste0("Chr", hot_chr, "_heat", ".pdf")
plotly::orca(p, here("analysis", "figures", fnsvg))
plotly::orca(p, here("analysis", "figures", fnpdf))
p
@

>>>>

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
p
@
